Secure Composition of Robust and Optimising Compilers

### 2023-07-08 popl/main.tex

The set of all properties can be partitioned into different {\em classes} ($\class$), i.e., safety, liveness, and neither safety or liveness~\cite{clarkson2008hyper}.
Given the central role for security, this paper focusses on safety properties.
Note that there are other classes $\class$ that contain more domain-specific properties, such as the class of memory safety properties.

@@

A {\em compiler} ($\cc{\src{L}}{\trg{L}}$) translates syntactic descriptions of programs from a {\em source} ($\src{L}$) into a {\em target} ($\trg{L}$) programming language.
%For the syntactic description of programs written in $\src{L}$, this paper writes $\src{\progvar}$, while for ones written in $\trg{L}$, this paper writes $\trg{\progvar}$.%\MP{not a fan of this sentence}
%This paper writes $\src{\progvar}$ and $\trg{\progvar}$ for programs written in $\src{L}$ and $\trg{L}$, respectively.
%      MK: I don't think we need to mention this at all
This translation is considered {\em correct} if it is semantics--preserving.
%That is, the compiler encodes any possible $\src{L}$--level feature in $\trg{L}$, such that the semantics are the same.
Unfortunately, correct compilers may be insecure compilers~\cite{patrignani2019survey}.
Programs translated by insecure compilers can violate security properties that the programmer assumes to hold. %, given the presence of a context--level program.
For a compiler to be secure, this paper makes use of the robust compilation framework~\cite{abate2019jour}, which we summarize in the following definition.
For \bul{compilers $\cc{\src{L}}{\trg{L}}$ to robustly preserve a class of properties $\class$}, consider \rul{properties $\pi$ of that class $\class$ and programs $\src{p}$ written in $\src{L}$} such that \iul{the program $\src{\progvar}$ robustly satisfies $\pi$}.
Then, \oul{$\cc{\src{L}}{\trg{L}}\left(\src{p}\right)$, the compiled version of $\src{\progvar}$, must robustly satisfy $\pi$}.

\begin{definition}[Robust Preservation]\label{def:rtp}
  Compiler $\cc{\src{L}}{\trg{L}}$ robustly preserves $\class$, \bul{$\rtp{\cc{\src{L}}{\trg{L}}}{\class}$}, iff \rul{for any $\pi\in\class$ and $\src{p}$} such that \iul{$\rsat{\src{\progvar}}{\pi}$}, it holds that \oul{$\rsat{\cc{\src{L}}{\trg{L}}\left(\src{p}\right)}{\pi}$}.
\end{definition}

>>>>

The set of all properties can be partitioned into different {\em classes} ($\class$), i.e., safety, liveness, and neither safety nor liveness~\cite{clarkson2008hyper}.
Given their central role for security, this paper focusses on safety properties.
% Note that there are other classes $\class$ that contain more domain-specific properties, such as the class of memory safety properties.
\MPin{
	remove.
	what does this sentence add? removing it does not remove any relevant information

@@

A {\em compiler} ($\cc{\src{L}}{\trg{L}}$) translates syntactic descriptions of programs from a {\em source} ($\src{L}$) into a {\em target} ($\trg{L}$) programming language.
%For the syntactic description of programs written in $\src{L}$, this paper writes $\src{\progvar}$, while for ones written in $\trg{L}$, this paper writes $\trg{\progvar}$.%\MP{not a fan of this sentence}
%This paper writes $\src{\progvar}$ and $\trg{\progvar}$ for programs written in $\src{L}$ and $\trg{L}$, respectively.
%      MK: I don't think we need to mention this at all
This translation is considered {\em correct} if it is semantics--preserving.
\MPin{
	i.e., ... brief desc?
}
%That is, the compiler encodes any possible $\src{L}$--level feature in $\trg{L}$, such that the semantics are the same.
Unfortunately, correct compilers may be insecure compilers~\cite{patrignani2019survey}, and programs translated by insecure compilers can violate security properties that the programmer assumes to hold. %, given the presence of a context--level program.
To define when a compiler is secure, this paper uses the robust compilation framework~\cite{abate2019jour}, which we summarize in the following definition.

To define robust compilation we only need the notion of a class of properties.
\MPin{define.}

For \bul{compilers $\cc{\src{L}}{\trg{L}}$ to robustly preserve a class of properties $\class$}, if for any \rul{property $\pi$ of that class $\class$ and programs $\src{p}$ written in $\src{L}$} we have that \iul{the program $\src{\progvar}$ robustly satisfies $\pi$}, then \oul{the compilation of $\src{\progvar}$, $\cc{\src{L}}{\trg{L}}\left(\src{p}\right)$, must robustly satisfy $\pi$}.

\begin{definition}[Robust Preservation]\label{def:rtp}
  % Compiler $\cc{\src{L}}{\trg{L}}$ robustly preserves $\class$, 
  \bul{$\rtp{\cc{\src{L}}{\trg{L}}}{\class}$}
  %, iff 
  $\isdef$
  \rul{for any $\pi\in\class$ and $\src{p}$} such that \iul{$\rsat{\src{\progvar}}{\pi}$}\MP{ use $\forall$}, it holds that \oul{$\rsat{\cc{\src{L}}{\trg{L}}\left(\src{p}\right)}{\pi}$}.
\end{definition}
